Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-12 paper/uist_2016/paper.tex
minor writing edits

\subsubsection{Rewinds and Photos}
When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo. In 50\% of cases, participants said they did. When they were shown the Rewind associated with that photo, nearly all participants knew the location captured---97\%. This result shows the impact of Rewind on memorability, as the addition images before and after the static photograph greatly impacts whether a past location is familiar to a user.

@@

We found that regular GPS users are less able to remember locations and trips, and more often rely on road signs to jog their memory or determine Rewind believability. This confirms Leshed et al.'s findings that GPS users are typically disengaged with their environment \cite{leshed2008car}. We found that while GPS users had lower remembrance overall, the group experienced a huge jump between location remembrance and trip remembrance, suggesting that Rewinds may actually engage GPS users' memories.

>>>>

\subsubsection{Rewinds and Photos}
When participants were shown a street side photo from their location history, they were asked whether they recognized the location in the photo. In 50\% of cases, participants said they did. When they were shown the Rewind associated with that photo, nearly all participants knew the location captured---97\%. This result shows the impact of Rewind on memorability, as the addition images before and after the static photograph changes whether a past location is familiar to a user.

@@

We found that regular GPS users are less able to remember locations and trips, and more often rely on road signs to jog their memory or determine Rewind believability. This confirms Leshed et al.'s findings that GPS users are typically disengaged with their environment \cite{leshed2008car}. We found that while GPS users had lower remembrance overall, the group experienced a jump between location remembrance and trip remembrance, suggesting that Rewinds may actually engage GPS users' memories.
